### 2020-04-19 Thesis-Chapter2-Background.tex
Work on international regs

@@

@@

This thesis is U.S.-focused, but \ac{EA} technologies and policies have international impacts. The following is a very
brief account of the regulatory environment in various jurisdictions around the world based primarily on a 2016 analysis
by the Library of Congress \cite{acosta_government_2016}.

@@

@@

    \country{Five-Eyes Countries}{acosta_government_2016}{
% UK, Australia, Canada
% UK Investigatory Powers Act \cite{legislature_2016}
% Australia In 2018 passed its Assistance and Access bill \cite{ag_2018}

@@

@@

    \country{Asian Countries}{acosta_government_2016}{
% China, Japan, Taiwan
% China Counterterrorism Law \cite{donahue_comparative_2018}

@@

    \country{Other Countries}{acosta_government_2016}{
% Brazil, Israel, South Africa
% Israel cybersecurity forensics and parnerships \cite{donahue_comparative_2018}

@@

% For more, read donahue_comparative_2018 (Israel and China) and budish_encryption_2018 (framework for analysis

@@

% There are several types of approaches:
% TODO: after defense, create table of these and reference it in \prop lists below
% - Allow strong encryption (anyone with the users' private keys can see it)
% - Disallow encryption (anyone can see it)
% - Make encryption sufficiently weak, e.g. limit key length (anyone with enough CPU can see it)
% - Require use of backdoored algorithms, security via obscurity (anyone with the secret knowledge can see it)
% - Allow any encryption, just be able to provide keys (anyone with the extra keys can see it)
%   - Store extra in gov't DBs, in corporate DBs, in third-party DBs, on blockchain, in secure HW on device
%   - Split the key and store it multiple places
% - Use some alternative path
%   - Coerced passwords, finding unencrypted copies, seizing devices while unlocked, lawful hacking

@@

\newcommand{\propsstart}[0]{\begin{itemize}}
\newcommand{\prop}[2]{\item \textbf{#1} \cite{#2}} % Proposal name, citation
\newcommand{\propsend}{\end{itemize}}

\propsstart
    \prop{Clipper chip/third-party key escrow}{press_1993}
% toasted by \cite{blaze_protocol_1994}
    \prop{Oblivious key escrow}{goos_oblivious_1996}
    \prop{Partial key escrow}{denning_taxonomy_1996}
\propsend

@@

\propsstart
    \prop{CLEAR}{ozzie_2018}
    \prop{Device escrow with HW}{savage_lawful_2018}
    \prop{Computational, blockchain approaches}{phan_key_2017}
\propsend

@@

\propsstart
    \prop{Lawful hacking}{nguyen_lawful_2017}
% see also \cite{soesanto_2018} \cite{kerr_encryption_2017}
    \prop{Forced password disclosure}{kerr_encryption_2017}
% see also \cite{bittenbender_2019}
    \prop{Alternative paths to plaintext}{kerr_encryption_2017}
% access device while unlocked; find copies elsewhere
\propsend

>>>>

This section includes both successful and failed cryptography regulation attempts in the U.S.

\subsubsection{Enacted U.S. Regulations}

@@

\subsubsection{Failed U.S. Regulation Attempts}

@@

This thesis is U.S.-focused, but \ac{EA} technologies and policies have international impacts. The following is a very
brief account of the regulatory environment in various jurisdictions around the world based primarily on a 2016 analysis
by the Law Library of Congress \cite{acosta_government_2016}.

@@

% What are the most relevant questions? Can the government--
% - Compel access to--
%   - all data?
%   - data encrypted by a service provider? Who are covered service providers?
% - Compel decryption of--
%   - all data?
%   - data encrypted by a service provider? Who are covered service providers?
% - Perform mass collection?
% - What legal limits are in place (e.g. warrants)?
% - What oversight is in place (e.g. inspectors general, public transparency)?
% - Does the government prescribe technical approaches?
% - Is the government explicitly allowed to engage in hacking?

@@

    \country{Five Eyes Countries}{acosta_government_2016}{

In 1946 The U.S. formalized an intelligence sharing operation with the U.K. in the BRUSA (now UKUSA) Agreement; over the
following 10 years, Australia, Canada, and New Zealand were made full partners to this agreement, which has become known
as ``Five Eyes'' \cite{nsa_2020}. Due to the close relationship between the intelligence and law enforcement agencies of
these countries, the member's encryption policies are relevant to one another.

% IDEA: put this in an appendix too? Or its own chapter? Too much detail for the background section.
%
% Looking at it now, even what I have seems like too much. Maybe move it all to an appendix.
%
% For more, read donahue_comparative_2018 (Israel and China) and budish_encryption_2018 (framework for analysis)
%
% Since the enactment of the Regulation of Investigatory Powers Act 2000, the U.K. government had the ability to serve
% written notices requiring mandated decryption. Law enforcement and intelligence agencies also have explicit permission
% to perform ``computer network exploitation,'' and approach this thesis refers to as ``\ac{lawful-hacking}.'' 2016's
% Investigatory Powers Act expanded these capabilities and, among other additions, in section 253 created ``technical
% capability notices'' that the Secretary of State can issue to telecommunications operators mandating \ac{EA}
% \cite{legislature_2016}.

The U.K. government has the explicit ability to force decryption, perform \ac{lawful-hacking}, and mandate \ac{EA}
though ``technical capability notices'' introduced in 2016's Investigatory Powers Act \cite{legislature_2016}. Australia
has weaker powers through a variety of laws, and in 2018 passed the Assistance and Access Act which created very similar
``technical capability notices'' \cite{ag_2018}. Canadian law requires cooperation between telecommunications providers
and law enforcement but does not directly address encryption. Canada has traditionally supported strong encryption, but
the pressure of \ac{the-cw2} is causing strain \cite{parsons_2019}.

@@

% TODO: it is very important to know who these requirements apply to. Traditional telecoms, obviously. Facebook and
% Google? Signal and WhatsApp?

France, Belgium, Germany, and Sweden require cooperation between telecommunications providers and law enforcement; for
France, Belgium, and Germany, that includes decrypting network traffic when possible. For Belgium, that decryption
capability is mandatory as of 2011. France, Germany, and Sweden each have some level of \ac{lawful-hacking} capability.
There is no E.U. legislation that requires key disclosure or decryption of network traffic.

@@

    \country{Asian Countries}{acosta_government_2016}{

Japanese authorities require cooperation and can request access to decrypted data, but subjects are not punished for
declining such requests. Taiwanese regulation does not specifically address encryption, but does mandate that
telecommunications providers provide interfaces ``with functions that can cooperate with interception.'' Chinese
authorities have great access to plaintext data by virtue of the political structure of the state, but its 2015
counter-terrorism law explicitly compels access to plaintext data upon request \cite{donahue_comparative_2018}.

% TODO: but you can still get iPhones in China, right... ? Again, scope?

@@

    \country{Other Countries}{acosta_government_2016}{

Brazil, South Africa, and Israel require cooperation between telecommunications providers and law enforcement. Brazil
law does not specifically address encryption, though it does require ``the technological resources necessary to suspend
telecommunications confidentiality in accordance with the law.'' South Africa mandates decryption when possible. Israeli
authorities can issue warrants for access to data or use warrantless orders similar to U.S. \ac{FISA} mechanisms. Israel
also has well developed \ac{lawful-hacking} capabilities and a centralized forensics laboratory
\cite{donahue_comparative_2018}.

@@

@@

% There are several types of approaches:
% TODO: after defense, create table of these and reference it in \prop lists below. This is better than sorting by
% historical origin.
% - Allow strong encryption (anyone with the users' private keys can see it)
% - Disallow encryption (anyone can see it)
% - Make encryption sufficiently weak, e.g. limit key length (anyone with enough CPU can see it)
% - Require use of backdoored algorithms, security via obscurity (anyone with the secret knowledge can see it)
% - Allow any encryption, just be able to provide keys (anyone with the extra keys can see it)
%   - Store extra in gov't DBs, in corporate DBs, in third-party DBs, on blockchain, in secure HW on device
%   - Split the key and store it multiple places
% - Use some alternative path
%   - Coerced passwords, finding unencrypted copies, seizing devices while unlocked, lawful hacking

There are several technical approaches to \ac{EA}. This section breaks down these approaches according to those
originating from \ac{the-cw1}, \ac{the-cw2}, and those that side-step the issue by using non-technical means to acquire
plaintext.

@@

\newcommand{\propsstart}[0]{\begin{itemize}}
% \newcommand{\prop}[2]{\item \textbf{#1} \cite{#2}} % Proposal name, citation
\newcommand{\prop}[3]{ % Name, citation, description
    \item \textbf{#1} \cite{#2} \nopagebreak

    \vspace{0.5\baselineskip} \parbox{\linewidth}{#3} \vspace{0.5\baselineskip}
}
\newcommand{\propsend}{\end{itemize}}

\propsstart
    \prop{Clipper chip/third-party key escrow}{press_1993}{}
% toasted by \cite{blaze_protocol_1994}
    \prop{Oblivious key escrow}{goos_oblivious_1996}{}
    \prop{Partial key escrow}{denning_taxonomy_1996}{}
\propsend

@@

\propsstart
    \prop{CLEAR}{ozzie_2018}{}
    \prop{Device escrow with HW}{savage_lawful_2018}{}
    \prop{Computational, blockchain approaches}{phan_key_2017}{}
\propsend

@@

\propsstart
    \prop{\Ac{lawful-hacking}}{nguyen_lawful_2017}{}
% see also \cite{soesanto_2018} \cite{kerr_encryption_2017}
    \prop{Forced password disclosure}{kerr_encryption_2017}{}
% see also \cite{bittenbender_2019}
    \prop{Alternative paths to plaintext}{kerr_encryption_2017}{}
% access device while unlocked; find copies elsewhere
\propsend
